Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
Added a comment
loosen layout rules
Changed a fig caption

\begin{table*}[]
	\centering
\begin{tabular}{c|p{11cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality compliant exploit certificate secured ``buffer overflow'' policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
``resource behaviour'' ``time behaviour'' efficient efficiency performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
``fault tolerance'' recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
	\caption{NFRs and associated signifiers -- \textsf{exp2}}
	\label{tbl:wnsig}

@@

%\todo[inline,color=green]{this table should have mysql}
\begin{table}[h]

@@

\begin{figure}[ht]
\centering
% \subfloat[MySQL]{
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
% \label{fig:subfig1}
% }
% \subfloat[MaxDB]{
% \includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
% \label{fig:subfig2}
% }
\caption[]{ROC value for the best learner per label. Possible values range from 0--1.
%\todo[inline]{better discussion}
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

Two perspectives to evaluate multi-label learners are with micro or macro measurements (used in Figure \ref{fig:mulan}).
Macro measurements are aggregated at a class or label level (per class) while micro measurements are at the element level (per element).
A macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. 
Unfortunately for MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels, see Figure \ref{fig:mulan}.

@@

\begin{figure*}[ht]
\centering
\subfloat[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfloat[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner. Possible values range from 0--1.
%\todo[inline]{better discussion}% and graphical legend would be nice}
}
\label{fig:mulan}
\end{figure*}

@@

\section{Limitations}
\label{sec:limit}
\subsection{Effectiveness}

>>>>

\begin{table*}
	\centering
\begin{tabular}{c|p{11cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality compliant exploit certificate secured ``buffer overflow'' policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
``resource behaviour'' ``time behaviour'' efficient efficiency performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
``fault tolerance'' recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
	\caption{NFRs and associated signifiers -- \textsf{exp2}}
	\label{tbl:wnsig}

@@

%\todo[inline,color=green]{this table should have mysql}
\begin{table}

@@

\begin{figure}
\centering
% \subfloat[MySQL]{
\includegraphics[width=0.45\textwidth]{figures/both-supervised}
% \label{fig:subfig1}
% }
% \subfloat[MaxDB]{
% \includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
% \label{fig:subfig2}
% }
\caption[]{ROC value for the best learner per label for MaxDB and MySQL. ROC values range from 0--1.
%\todo[inline]{better discussion}
}
\label{fig:best-learn-per-tag}
\end{figure}

@@

Two perspectives to evaluate multi-label learners are with micro or macro measurements (used in Figure \ref{fig:mulan}).
Macro measurements are aggregated at a class or label level (per class) while micro measurements are at the element level (per element).
A macro-ROC measurement is the average ROC over the ROC values for all labels, where a micro-ROC is the average ROC over all examples that were classified. 
Unfortunately for MaxDB, the macro-ROC values are undefined because of poor performance of one of the labels.%, see Figure \ref{fig:mulan}.

@@

\begin{figure*}
\centering
\subfloat[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfloat[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner. Possible values range from 0--1.
%\todo[inline]{better discussion}% and graphical legend would be nice}
}
\label{fig:mulan}
\end{figure*}

@@

\section{Limitations}
\label{sec:limit}

%XXX can just remove this
\subsection{Effectiveness}
